---
title: "Project Details"
output: 
  html_fragment
params:
  ie_data: NA
---

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(fontawesome)
```

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning =  FALSE, message = FALSE, skimr_include_summary = FALSE)
data <- params$ie_data
```

::: {.section}
INTERVENTION 
:::

::: {.title}
`r data[, "prog_name"]`
:::


::::: {class='fluid-row distable'}

::: {class='col-sm-4 colinfo'}
`r fa("list-alt", fill = "#9bd3cc", height = "3em")` <br>
[BASIC PROGRAM INFORMATION]{.coltitle} <br>
 <br>
[COUNTRY]{.infotitle} <br>
[`r data[, "country"]`]{.infotext} <br>
[REGION]{.infotitle} <br>
[`r data[, "region"]`]{.infotext} <br>
[LEAD IMPLEMENTING AGENCY]{.infotitle} <br>
[`r data[, "leadname"]`]{.infotext} <br>
[TYPE LEAD IMPLEMENTING AGENCY]{.infotitle} <br>
[`r data[, "lead"]`]{.infotext}

:::

::: {class='col-sm-4 colinfo'}
`r fa("address-card", fill = "#9bd3cc", height = "3em")` <br>
[PARTICIPANT PROFILE]{.coltitle} <br>
 <br>
[TARGETED POVERTY GROUPS]{.infotitle} <br>
[`r data[, "pov_seg"]`]{.infotext} <br>
[PRIORITY VULNERABLE GROUPS]{.infotitle} <br>
[`r data[, "priority_group"]`]{.infotext}

:::

::: {class='col-sm-4 colinfo'}
`r fa("users", fill = "#9bd3cc", height = "3em")` <br>
[PROGRAM COVERAGE]{.coltitle} <br>
 <br>
[TOTAL NUMBER OF BENEFICIARIES]{.infotitle} <br>
[`r data[, "total_beneficiary"]`]{.infotext} <br>
[AREAS]{.infotitle} <br>
[`r data[, "area"]`]{.infotext} <br>
[GEOGRAPHIC COVERAGE]{.infotitle} <br>
[`r data[, "geo_cov"]`]{.infotext}

:::

:::::

<br>

::: {.section}
IMPACT EVALUATION 
:::

::: {.title}
`r data[, "ie_name"]`
:::

::::: {class='fluid-row distable'}

::: {class='col-sm-9 colsum'}

::: {.title2}
SUMMARY
:::

`r data[, "ie_summary"]`

::: {.title2}
RESEARCH QUESTION(S)
:::


::: {class='researchq'}

```{r}
question <- 
  str_replace_all(
    data[, "ie_questions"],
    "<br>", 
    "<br><b>&#10148;</b> "
  ) 

question <- 
  paste(
    "<b>&#10148;</b>", 
    question, 
    sep= " "
    )
```

`r question`

:::

:::

::: {class='col-sm-3 colpi'}
<br>
`r fa("book-reader", fill = "#4c7ca3", height = "3em", width = "3em")`
<br>
[PRINCIPAL INVESTIGATORS]{.pititle}
<br>
[`r data[, "pi_list"]`]{.pitext}
<br>
<br>
`r fa("calendar-alt", fill = "#4c7ca3", height = "3em", width = "3em")`
<br>
[TIMELINE]{.pisection}
<br>
[Baseline results: `r data[, "baseline_results"]`]{.pitext}
<br>
[Final results: `r data[, "final_results"]`]{.pitext}

:::

:::::

<br>

::: {.title2}
IDENTIFICATION STRATEGY 
:::

```{r}
# Code to choose the image to display
# Initialize the folder that contains the picture
folder <- "www/"
if (str_detect(data$ie_method,"Randomized Controlled Trial")) {
  rct_img = paste0(folder, "rct.png")
} else {
  rct_img = paste0(folder, "rct_gray.png")
}

if (str_detect(data$ie_method,"DIFFERENCE-IN-DIFFERENCES")) {
  did_img = paste0(folder, "did.png")
} else {
  did_img = paste0(folder, "did_gray.png")
}

if (str_detect(data$ie_method,"INSTRUMENTAL VARIABLE")) {
  iv_img = paste0(folder, "iv.png")
} else {
  iv_img = paste0(folder, "iv_gray.png")
}

if (str_detect(data$ie_method,"MATCHING")) {
  matching_img = paste0(folder, "matching.png")
} else {
  matching_img = paste0(folder, "matching_gray.png")
}

if (str_detect(data$ie_method,"REGRESSION DISCONTINUITY DESIGN")) {
  rdd_img = paste0(folder, "rdd.png")
} else {
  rdd_img = paste0(folder, "rdd_gray.png")
}

if (str_detect(data$ie_method,"OTHER")) {
  other_img = paste0(folder, "other.png")
} else {
  other_img = paste0(folder, "other_gray.png")
}
```

::::::::: {class='fluid-row idenstrat'}

::: {class='col-sm-2 method'}

![rct](`r rct_img`) 
<br>
[RANDOMIZED CONTROLLED TRIAL]{.methodtext}

:::

::: {class='col-sm-2 method'}

![did](`r did_img`)
<br>
[DIFFERENCE-IN-DIFFERENCES]{.methodtext}

:::

::: {class='col-sm-2 method'}

![iv](`r iv_img`)
<br>
[INSTRUMENTAL VARIABLE]{.methodtext}

:::

::: {class='col-sm-2 method'}

![matching](`r matching_img`)
<br>
[MATCHING]{.methodtext}

:::

::: {class='col-sm-2 method'}

![rdd](`r rdd_img`)
<br>
[REGRESSION DISCONTINUITY DESIGN]{.methodtext}

:::

::: {class='col-sm-2 method'}

![other](`r other_img`)
<br>
[OTHER]{.methodtext}

:::

:::::::::

<br>

::: {.title2}
LEARNING PRIORITIES 
:::

```{r}
# Code to choose the image to display
# Initialize the folder that contains the picture
folder <- "www/"
if (str_detect(data$learning_p,"Cost-effectiveness of large-scale government-led programs")
    || str_detect(data$learning_p,"Spillovers and general equilibrium effects")
    ) {
  img_lp1 = paste0(folder, "effectiveness.PNG")
} else {
  img_lp1 = paste0(folder, "effectiveness_gray.PNG")
}

if (str_detect(data$learning_p,"Scalability, impact and cost-effectiveness")) {
  img_lp2 = paste0(folder, "modality.PNG")
} else {
  img_lp2 = paste0(folder, "modality_gray.PNG")
}

if (str_detect(data$learning_p,"How impacts vary over time")) {
  img_lp3 = paste0(folder, "time.PNG")
} else {
  img_lp3 = paste0(folder, "time_gray.PNG")
}

if (str_detect(data$learning_p,"Optimal bundle/marginal contribution of bundled interventions")
    || str_detect(data$learning_p,"Timing, sequencing, and intensity of bundled interventions")
    ) {
  img_lp4 = paste0(folder, "bundling.PNG")
} else {
  img_lp4 = paste0(folder, "bundling_gray.PNG")
}

if (str_detect(data$learning_p,"Cost-effectiveness across population groups")
    || str_detect(data$learning_p,"Increasing cost-effectiveness for sub-groups")
    ) {
  img_lp5 = paste0(folder, "targeting.PNG")
} else {
  img_lp5 = paste0(folder, "targeting_gray.PNG")
}

if (str_detect(data$learning_p,"Adapting programs to urban contexts")
    || str_detect(data$learning_p,"Adapting programs to fragile contexts")
    ) {
  img_lp6 = paste0(folder, "external.PNG")
} else {
  img_lp6 = paste0(folder, "external_gray.PNG")
}

if (str_detect(data$learning_p,"Effects on resilience and mechanisms")) {
  img_lp7 = paste0(folder, "resilience.PNG")
} else {
  img_lp7 = paste0(folder, "resilience_gray.PNG")
}

if (str_detect(data$learning_p,"Other")) {
  img_lp8 = paste0(folder, "other_lp.png")
} else {
  img_lp8 = paste0(folder, "other_lp_gray.png")
}
```


::::::: {class='fluid-row idenstrat'}

::: {class='col-sm-3 learning'}
![lp1](`r img_lp1`) 
<br>
[EFFECTIVENESS AT SCALE]{.methodtext}
:::

::: {class='col-sm-3 learning'}

![lp2](`r img_lp2`)
<br>
[SCALABLE DELIVERY MODALITY]{.methodtext}
:::

::: {class='col-sm-3 learning'}
![lp3](`r img_lp3`)
<br>
[DYNAMICS OVER TIME]{.methodtext}
:::

::: {class='col-sm-3 learning'}
![lp4](`r img_lp4`)
<br>
[BUNDLING OF INTERVENTIONS]{.methodtext}
:::

:::::::

::::::: {class='fluid-row idenstrat'}

::: {class='col-sm-3 learningdetails'}
- What is the cost-effectiveness of large-scale government-led programs? 
- What is the nature and extent of spillovers on the local economy and general equilibrium effects?
:::

::: {class='col-sm-3 learningdetails'}
- How do alternative delivery modalities that enhance scalability affect program impact and cost-effectiveness?
:::

::: {class='col-sm-3 learningdetails'}
- How do impacts vary over time?  Are they sustained in the short to long-term? How does it affect cost-benefit analysis?
:::

::: {class='col-sm-3 learningdetails'}
- What is the marginal contribution of constituent interventions (including cash) to overall impact and overall cost? What is the minimum appropriate bundle or optimal bundle for a given context?
- Does the timing, sequencing, and intensity of interventions matter?
:::

:::::::

::::::: {class='fluid-row idenstrat'}

::: {class='col-sm-3 learning'}
![lp5](`r img_lp5`)
<br>
[TARGETING/HETEROGENEITY]{.methodtext}
:::

::: {class='col-sm-3 learning'}
![lp6](`r img_lp6`)
<br>
[EXTERNAL VALIDITY ACROSS SETTINGS]{.methodtext}
:::

::: {class='col-sm-3 learning'}
![lp7](`r img_lp7`)
<br>
[RESILIENCE AND SHOCK RESPONSIVENESS]{.methodtext}
:::

::: {class='col-sm-3 learning'}
![lp8](`r img_lp8`)
<br>
[OTHER]{.methodtext}
:::

:::::::

::::::: {class='fluid-row idenstrat'}

::: {class='col-sm-3 learningdetails'}
- What is the cost-effectiveness of economic inclusion programs across population groups?
- What modifications in bundle design and delivery are necessary to increase cost-effectiveness for different sub-groups?
:::

::: {class='col-sm-3 learningdetails'}
-	How to adapt economic inclusion programs in urban contexts?
- How to adapt economic inclusion programs in FCS and displacement affected contexts?
:::

::: {class='col-sm-3 learningdetails'}
- Do economic inclusion programs improve households' resilience to (climate, conflict, or economic) shocks? How?
:::

::: {class='col-sm-3 learningdetails'}

:::
:::::::

